What to Expect with Life Expectancy?

### 2024-12-04 paper/paper.qmd
Add files via upload

For the developed countries model, predictors like Diphtheria Immunization, Schooling, Total Expenditure, and the number of Doctors per 10,000 were included. These variables are well-established factors influencing life expectancy in high-income nations [@life_expectancy_who; @world_health_statistics]. In the developing countries model, additional predictors such as Schooling, and healthcare access variables like Doctors and Nurses per 10,000 were added to account for differences in healthcare infrastructure.

@@

```{r}
#| label: tbl-keyestimates
#| tbl-cap: "Summary of key model estimates for Developed and Developing counties, including coefficients for predictors like Diphtheria, Schooling, and TotalExpenditure, pct_doctor, pct_nursing, with standard errors for each estimate. Model performance statistics, such as sample size, R², and adjusted R², are also displayed."
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

A comparison of predicted life expectancy distributions reveals several notable trends. Longer schooling years[@fig-schoolgroups] strongly correlate with higher life expectancy, highlighting the critical role of education. High diphtheria immunization coverage[@fig-diphtheria-groups] generally predicts greater life expectancy, though medium and low coverage levels exhibit variability, suggesting that immunization is not the sole or dominant factor. Similarly, higher government health expenditure[@fig-totalexpenditure-groups] aligns with improved outcomes, while lower spending shows minimal variation. Availability of doctors and nurses[@fig-doctornursing-groups] also indicates a positive relationship with life expectancy, though some variability suggests other contributing factors are at play.

>>>>

For the developed countries model, predictors like Diphtheria Immunization, Schooling, Health Expenditure, and the number of Doctors per 10,000 were included. These variables are well-established factors influencing life expectancy in high-income nations [@life_expectancy_who; @world_health_statistics]. In the developing countries model, additional predictors such as Schooling, and healthcare access variables like Doctors and Nurses per 10,000 were added to account for differences in healthcare infrastructure.

@@

```{r}
#| label: tbl-keyestimates
#| tbl-cap: "Summary of key model estimates for Developed and Developing counties, including coefficients for predictors like Diphtheria, Schooling, and Percentage of HealthExpenditure, pct_doctor, pct_nursing, with standard errors for each estimate. Model performance statistics, such as sample size, R², and adjusted R², are also displayed."
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

A comparison of predicted life expectancy distributions reveals several notable trends. Longer schooling years strongly correlate with higher life expectancy, highlighting the critical role of education. High diphtheria immunization coverage generally predicts greater life expectancy, though medium and low coverage levels exhibit variability, suggesting that immunization is not the sole or dominant factor. Similarly, higher percentage of government health expenditure aligns with improved outcomes, while lower spending shows minimal variation. Availability of doctors and nurses also indicates a positive relationship with life expectancy, though some variability suggests other contributing factors are at play.
